\documentclass[10pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{verbatim}
\usepackage{hyperref}

\pagestyle{empty}
\geometry{letterpaper,tmargin=0.5in,bmargin=0.5in,lmargin=0.5in,rmargin=0.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Michael Gerow}
\newcommand{\phone}{918-740-1775}
\newcommand{\email}{\href{mailto:gerow@usc.edu?subject=Hello}{gerow@usc.edu}}
\newcommand{\linkedin}{\href{http://www.linkedin.com/in/gerow}{http://www.linkedin.com/in/gerow}}
\newcommand{\website}{\href{http://mgerow.com}{http://mgerow.com}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\Large\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

\newcommand{\resplainsection}[1]{
	{\fontfamily{phv}\selectfont\Large#1}
	\vspace{-12pt}
	\\

}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

\newcommand{\resshortbigitem}[2]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2
}

\newcommand{\resveryshortbigitem}[1]{
	\vspace{-5pt}
	\item
	\textbf{#1}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

\newenvironment{resshortsubsec}[2]{
	\resshortbigitem{#1}{#2}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

\newenvironment{resveryshortsubsec}[1]{
	\resveryshortbigitem{#1}
	\vspace{-2pt}
	\begin{itemize}
}{
    \end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \email; \linkedin \hfill \website; \phone}

\vspace{8 pt}


%%%%%%%%%%%%%%%%%%%%%%%%
\resplainsection{Professional Summary}
	A National Merit Scholar Computer Engineering and Computer Science student at USC with over four years of programming experience and nearly a year of experience working in a professional setting including working on internal IT applications and embedded set top box applications.  A two year member of the USC Autonomous Underwater Vehicle team competing in the AUVSI RoboSub event.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

	\begin{ressubsec}{University of Southern California}{Los Angeles, CA}{Majoring in Computer Engineering and Computer Science}
		\ressubitem{University GPA:  3.5, Major GPA: 3.9}
		\ressubitem{Presidential Scholar}
		\ressubitem{Projected Graduation Date:  May, 2014}
	\end{ressubsec}

\end{ressection}

\begin{ressection}{Technical Summary}

	\resitem{\textbf{Languages:} C, C++, Java, Go, Python, Verilog, \LaTeX, Motorola 68000 Assembly }
	\resitem{\textbf{Libraries/Frameworks:} OpenGL, ROS (Robot Operating System), OpenCV, Berkeley Sockets }
	\resitem{\textbf{Systems/Tools:} Linux and Unix variants (Debian, Ubuntu, Solaris), OSX, Windows 2000/XP/Vista/7, SVN, Git, Mercurial, MongoDB, MySQL, Eclipse, Multithreaded Environments (Using Agents)}
	
\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Professional Experience}
	%\begin{ressubsec}{Car Country}{Tulsa, OK}{Currier December 2010--January 2011 (Winter Break)}
	%	\ressubitem{Transported documents and payments to and from businesses and banks.}
	%\end{ressubsec}
	\begin{ressubsec}{DIRECTV}{El Segundo, CA}{Software Engineering Intern May 2012--August 2012}
		\ressubitem{Embedded systems work with set top box UI in Java}
		\ressubitem{Created tool to increase productivity when working with set top box assets}
	\end{ressubsec}
	\begin{ressubsec}{Nelson Auto Group}{Tulsa, OK}{Information Technology Intern May 2011--August 2011, December 2011--January 2012}
		\ressubitem{Created a system to effectively and efficiently keep copies of all physical media needed for the company's computer and technical systems.}
		\ressubitem{Created a system to allow managers to easily access recorded calls through a web interface using PHP to access Asterisk servers.}
	\end{ressubsec}

	%\resbigitem{Christ the King Parish}{Tulsa, OK}{Maintainance:  March 2008--August 2010}
		%\ressubitem{Ensured proper upkeep of church and affiliated school, helped facilitate events, and repaired utilities.}
	%\end{ressubsec}
	
	\begin{comment}
	\begin{ressubsec}{Tulsa Day Center For the Homeless}{Tulsa, OK}{Volunteer:  July 2006--September 2009}
		\ressubitem{Worked mainly with individuals receiving tuberculosis tests.}
		\ressubitem{Entered tuberculosis data and kept computerized records between the Day Center for the Homeless and the Tulsa City-County Health Department up to date.}
	\end{ressubsec}
	\end{comment}

\end{ressection}

\begin{ressection}{Projects Outside of School}
    \begin{resveryshortsubsec}{Projects Created/Forked}
        \ressubitem{\emph{Boop}: Lightweight Go server for running commands in response HTTP actions.  Very good for throwing together quick solutions when needed. \url{https://github.com/gerow/boop}}
        \ressubitem{\emph{gnome-shell-google-calendar}: Fork of script to allow Google Calendar integration into GNOME 3. Added ability to use within GNOME 3 under Ubuntu. \url{https://github.com/gerow/gnome-shell-google-calendar}}
        \ressubitem{\emph{btcreg}: A service for aliasing bitcoin addresses agains email addresses. Mainly created in order to play around with creating database driven web applications using Go and MongoDB.  \url{https://github.com/gerow/btcreg}}
        \ressubitem{\emph{This Resume}: Yes, even this resume is written in \LaTeX. \url{https://github.com/gerow/resume}}
    \end{resveryshortsubsec}
    \begin{resveryshortsubsec}{Projects Done With Others}
        \ressubitem{\emph{LittleNote}: An iPhone app for sending notes to your significant other.  Worked on backend side implemented as a Ruby on Rails application. \url{https://github.com/kcbarry/LittleNoteWeb}}
    \end{resveryshortsubsec}
    \begin{resveryshortsubsec}{Projects Contributed To}
        \ressubitem{\emph{Goose}: Database migration tool for Go. Added sqlite3 support. Currently working on support for applications that wish to target multiple database types. \url{https://bitbucket.org/liamstask/goose}}
    \end{resveryshortsubsec}
\end{ressection}

\begin{ressection}{Club Experience}
	\begin{ressubsec}{USC Autonomous Underwater Vehicle Team}{Los Angeles, CA}{Member of Software Team September 2010--May 2012}
		\ressubitem{Wrote C++ code for robot running within the ROS environment under Ubuntu.}
		\ressubitem{Gained experience working with vision processing using OpenCV.}
	\end{ressubsec}
\end{ressection}

%\begin{ressection}{Relevant coursework}
	%\resshortbigitem{Computer Science 101}{Introduction to Computer Science}
	%\resshortbigitem{Computer Science 102}{Data Structures}
	%\resshortbigitem{Electrical Engineering 101}{Introduction to Digital Logic}
%	\resshortbigitem{\emph{In Progress:} Computer Science 271}{Discrete Mathematics}
%	\resshortbigitem{\emph{In Progress:} Electrical Engineering 450}{Networking}
%	\resshortbigitem{\emph{In Progress:} Electrical Engineering 457}{Computer System Organization}
%	\resshortbigitem{Computer Science 201}{Software Development}
%	\resshortbigitem{ Electrical Engineering 357}{Computer Architecture}
%	\resshortbigitem{Compuer Science 200}{Object-Oriented Programming}
%	\resshortbigitem{Computer Science 480}{Computer Graphics}
%	\resshortbigitem{Electrical Engineering 201}{Introduction to Digital Circuits}
%\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{ressection}{Interests}
%	\begin{comment}
%	\resitem{\textbf{Game Development:}  Currently working on a project to create a 2d game engine in Java using OpenGL.  Hope to eventually use the engine to make some kind of %Metroid inspired platformer.  Also working with a team of four other people on a project to create a real time strategy game using the Unity game engine.}
%	\resitem{\textbf{Typesetting:} Working on an application called Baseline which is intended to allow more people to take advantage of the power of \LaTeX without needing to learn all %the markup.} 
%	\resitem{\textbf{Amateur Radio:}  A federally licensed amateur radio operator.}
%	\end{comment}
%	\resitem{\textbf{Robotics:} Currently a member of USC's robotics team working on vision processing for an autonomous underwater vehicle}
%\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{ressection}{Achievements}

	%\resitem{Currently a member of the software team for USC's Seabee3 underwater autonomous vehicle working with computer vision.}

%	\resitem{National Merit Scholar.}
	
%	\resitem{Created a factory simulation with a team of 18 people for a class project.}
	
	%\resitem{Head of Bishop Kelley High School robotics electrical/software team during 2010.}

%\end{ressection}


\end{document}
